\documentclass[a4paper]{exam}

\usepackage{amsmath,amsfonts}
\usepackage{geometry}

\printanswers

\title{Weekly Challenge 03: Comparison-based Sorting Algorithms}
\author{CS 412 Algorithms: Design and Analysis}
\date{Spring 2022}

\begin{document}
\maketitle

\begin{questions}
  
\question We want to compare various comparison-based sorting algorithms. More specifically, we want to compare the number of comparisons performed by each algorithm.

  \noindent\textbf{TASK}: Obtain or write implementations of various comparison-based sorting algorithms: insertion, selection, quick, merge, and/or any others. Modify the implementations so as to obtain a count of the total number of comparisons performed for a given input.

  \noindent\textbf{TASK}: For a given $n$, generate $\frac{n}{10}$ random permutations of the set, $\{1,2,\ldots,n\}$, and obtain the number of comparisons performed by each algorithm to sort each permutation. For each algorithm, obtain the average number of comparisons over its $\frac{n}{10}$ runs.

  \noindent\textbf{TASK}: Include below, a plot of the average number of comparisons obtained above for all the algorithms over a wide range of values of $n$, e.g. $\{100n \mid n\in [1,500] \}$. Also include any observations or insights that you find worth mentioning.

  \noindent\textbf{TASK}: Share your plot as a comment on the \textit{Week 03 Challenge} post in the course group on Yammer.

  \begin{solution}
    % Enter your solution here.
  \end{solution}


\end{questions}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
